%!TEX root = main.tex
\chapter{Architectural tactics}
As part of this course the main tactics that we have considered is \emph{modifiability}, \emph{availability}, \emph{performance}, \emph{testability}, \emph{usability} and \emph{security}.

The application is not considered to be high risk target, nor does it contain critical information. Because of this, security is not a tactic that will be considered. To further limit the scope of this assignment, performance has not been a focus area. This is justifiable as the game that is to be developed is rather simple and performance should not pose an issue.

    \section{Modifiability}
    The code is divided up into several different objects and classes in order to separate code changes so that it only affects the objects and classes being changed. This is done to avoid a ripple effect, i.e. the need to change other related components or modules in the architecture when one part of the game is changed\cite[p.~107]{pensum}. Internal variables should generally be held private, and access to different objects and classes are made through public methods. Objects for boats are made as general as possible to prevent major code changes when initializing a new boat. By just changing some attributes to the common object, one can make a new boat with a given size and colour. 
    
    \section{Availability}
    \label{avail}
    In order to maintain a high degree of availability, LaHAW will implement and handle common exceptions where necessary. This tactic is fast and simple to implement, ensuring a comprehensive architectural design. The project has a limited time frame, and the architecture will reflect that.
    
    % \section{Performance}
    % Performance is not the main focus area of LaHAW, but response time during the game should be as short as possible to give a smooth user interaction. Java does most of the garbage collection, so the goal is to limit the amount of allocated objects at once. In addition, one can increase computational efficiency by making efficient algorithms in critical areas. 
    
    \section{Testability}
    \label{test}
    As per the MVC pattern requirements, the user interface and game logic is held separated, which in turn increases testability. In addition to this, the modifiability tactics require further separation of different sections, with control over input and output. A built-in monitor of CPU usage and memory load will ensure that the program runs smoothly while avoiding memory leaks.
    
    Use of singletons can be a detriment to testability, especially considering unit testing\cite{online:msdn_singleton}, but the use of such classes are to be held at a minimum.

    \section{Usability}
    Usability is achieved by separate the user interface from rest of the application. MVC is chosen as the main architectural pattern to support modification to the user interface without affecting other parts of the system. During configure time, the user gives the system a model of their experience level by selecting a difficulty level.
    
    The game will implement a hint system where, during run-time, the game will present hints that shall help the user in understanding the game rules and how to interact with our implementation of the game. This to support usability by giving the user more confidence in their choices.  These hints are related to the difficulty level chosen by the user at configure-time.
    
    % \section{Security}
    % LaHAW will not authorize or authenticate users as it require no personal information or other personal details to play. The game is not seen as susceptible to attacks from external sources, and does not send out any information from the device. Therefore, the architecture will not focus much on security in regards of encryption and access limitation. As mentioned above, there is a limited time frame from now to the project deadline, and other tactics have a greater priority.